---
title: "AK-Map"
author: "Anna Talucci"
date: "1/22/2020"
output: html_document
---

# Packages
```{r include=FALSE}
  library(leaflet)
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(DT)
library(sp)
  library(sf)
  library(ggmap) # devtools::install_github("dkahle/ggmap")
library(ggrepel)
library(RStoolbox)
library(raster)
library(rgdal)

library(RColorBrewer)
library(cowplot)
library(ggspatial)
library(maps)
```
- UL -159.2085, 71.3877
- UR -153.6549, 71.3877
- LR -153.6549, 70.3104
- LL -159.2085, 70.3104

```{r}

(insetrect <- data.frame(xmin = -153.6549, xmax = -159.2085,
    ymin = 70.3104, ymax = 71.3877))
```
```{r}
proj_ak_shape = "+proj=longlat +datum=NAD83 +no_defs"
```

```{r}
proj4string(insetrect) <-CRS("+proj=longlat +datum=NAD83 +no_defs")

```

Utqiavik, AK (AKA Barrow, AK)
```{r}
labs <- tibble(
  long = c(-156.7886),
  lat = c(71.2906),
  names = ("Utqiagvik")) 
```

# AK Vector

```{r}
ak_sf <- st_read(
  "../data/AK-state/GU_StateOrTerritory.shp")
```

```{r}
ak_sp = readOGR("../data/AK-state/GU_StateOrTerritory.shp", "GU_StateOrTerritory") 
```
```{r}
plot(ak_sp)
```


```{r}
st_crs(ak_sf)

```



```{r}
ak_sp_ee = spTransform(ak_sp, CRS( "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
```
+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs 


```{r}
ak_sp_3338 = spTransform(ak_sp, CRS( "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"))
```

```{r}
ak_ee = st_transform(ak_sf, CRS( "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
```


```{r}
ak_sf_eeak = st_transform(ak_sf, CRS( "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"))
```

+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs 
+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs 

```{r}
ak_sp_eeak = spTransform(ak_sp, CRS( "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"))
```


```{r}
ak_sp_3338 = spTransform(ak_sp, CRS( "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"))
```


```{r}
ak_sp_wgs84 = spTransform(ak_sp, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
plot(ak_sp_wgs84)
```

```{r}
plot(ak_sp_ee)
```
EPSG 3338 NAD83 / Alaska Albers
```{r}
plot(ak_sp_3338)
```
Alaska Albers Equal Area Conic
```{r}
plot(ak_sp_eeak)
```
```{r}
structure(ak_sf_eeak)
```
From ak_raster_3338 -214588.4, 23414.28, 2212535, 2399715  (xmin, xmax, ymin, ymax)
```{r}
map_ak1 = ggplot() + 
  geom_sf(data = ak_sf_eeak, fill = "#E8E8E8", color = "black") +
  geom_rect(data = insetrect, aes(xmin = -214588.4, xmax = 23414.28, ymin = 2212535, ymax = 2399715), alpha = 0, colour = "#000080", size = 1, linetype = 1) +
  xlab("")+ylab("")+
  coord_sf() +
  theme_void() +
 # add a bounding box so that will border the inset
 theme(panel.background = element_rect(colour = "black", fill = "white", size = 0.5))


map_ak1
```
```{r}
map_ak2 = ggplot() + 
  geom_sf(data = ak_sf, fill = "#E8E8E8", color = "black") +
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) +
  xlab("")+ylab("")+
  coord_sf() +
  theme_void() +
 # add a bounding box so that will border the inset
 theme(panel.background = element_rect(colour = "black", fill = "white", size = 0.5))


map_ak2
```
# AK Raster Data



```{r}
ak_raster = raster("../data/raster/S2_AK-2.tif")
```

```{r}
projection(ak_raster)
```

```{r}
newproj = "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
```


```{r}
ak_raster_3338 <- projectRaster(ak_raster, crs=newproj)


```


```{r}
structure(ak_raster_3338)
```




```{r}
ak_stack <- stack("../data/raster/S2_AK-2.tif")
```

```{r}
ak_brick <- brick("../data/raster/S2_AK-2.tif")
```


```{r}
ak_stack
```

```{r}
ak_stack@layers
```

```{r}
ak_brick_3338 <- projectRaster(ak_brick, crs=newproj)


```

From ak_raster_3338 -214588.4, 23414.28, 2212535, 2399715  (xmin, xmax, ymin, ymax)
{bands: ['B12', 'B11', 'B4'], min: 0, max: 1, gamma: 1.5}
```{r}
plotRGB(ak_stack,
        r = 1, g = 2, b = 3,
        stretch = "lin")

```

```{r}
extent(ak_stack)
```

```{r}
summary(ak_stack)
```

```{r}
plot_raster = ggplot() + ggRGB(ak_stack, r=1, g=2, b=3, stretch = "lin", ggLayer = TRUE, coord_equal = TRUE) +
  xlim(-159.4999, -153.4058) + ylim(69.89028, 71.52341) +
  theme_void() +
   theme(
     axis.text = element_blank(),
     axis.ticks = element_blank(),
     axis.title = element_blank()) +
  
  annotation_scale(location = "br", width_hint = 0.25, text_size = 12, text_face = NULL, text_family = "serif", text_col = "black") +
    annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.4, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_minimal(line_width = 1, line_col = "white", fill = "white", text_size = 10, text_face = NULL, text_family = "serif", text_col = "black")) +
  coord_sf(crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0", xlim = c(-159.4999, -153.4058), ylim = c(69.89028, 71.52341), expand = TRUE)

plot_raster

```

```{r}
plot_raster1 = ggplot() + ggRGB(ak_stack, r=1, g=2, b=3, stretch = "lin", ggLayer = TRUE, coord_equal = TRUE) +
  xlim(-159.4999, -153.4058) + ylim(69.89028, 71.52341) +
  theme_void() +
   theme(
     axis.text = element_blank(),
     axis.ticks = element_blank(),
     axis.title = element_blank()) 

plot_raster1

```

# Map for AK proposal

```{r fig.height=4, fig.width=6}
ak_map = ggdraw() +
   draw_plot(plot_raster1) +
  draw_plot(map_ak1, x = 0.05, y = 0.02, width = .35, height = .35) 
ak_map
```


```{r}
ggsave("../figures/ak-map.png", plot = ak_map, width = 6, height = 4, dpi = 600)
```




